### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex
more writing

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed. This includes which classifiers and data sets where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.

% Which classifiers and data sets used
The classifiers considered for a recommended ranking were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods. The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}. They where all used in their default configurations as specified by WEKA.

datasets

@@

% How rest of the evaluation carried out
All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) and 12 GB RAM. It is notable that especially the time-related results are to be viewed in regard to this setup. No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set. As n = 448 in this case, the full results are not included in the discussion of the results. They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.

>>>>

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed. This includes which classifiers, data sets and meta features where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.

% Which classifiers 
The classifiers considered in the rankings were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods. The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}. They where all used in their default configurations as specified by WEKA.

% Which data sets
Data sets for the analysis where gathered from OpenML. From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved and with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand where selected. Only data sets with a defined, nominal target feature that are in the .ARFF format and where not specifically designed for streaming analysis\footnotemark{} where considered, which resulted in a reduced selection of 812 instances. Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features where removed as well, leading to a final selection of 448 data sets. Even though evaluation was only carried out on the shorter list, both the list of 812 and 448 data sets are included in the supplementary material for completeness.

\footnotetext{Data sets that contained the substring 'BNG' for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network\cite{van2014algorithm} for the sake of data stream analysis where not included in the evaluation.}

% Which meta features
As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used. Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew. Meta features where calculated with the help of an implementation provided by OpenML .Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.

@@

% How rest of the evaluation carried out
All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) and 12 GB RAM. It is notable that especially the time-related results are to be viewed in regard to this setup. No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set. As n = 448 in this case, the detailed values for each data set are not included in the discussion of the results. They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.
